---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BrokkR

<!-- badges: start -->
<!-- badges: end -->

This package allows users to provide a list of URLs for webpages of interest and creates a dataframe with Bag of Words representation that can then later be fed into a machine learning model of their choice. Users also have the option to produce a dataframe with just the raw text of their target webpages to apply the text representation of their choice instead.

## Features

The pymine package includes the following four functions:

-   `create_id()`: Takes a vector of webpage urls formatted as strings as an input and returns a vector of unique string identifiers for each webpage based on their url. The identifier is composed of the main webpage name followed by a number.
-   `text_from_url()` : Takes a vector of urls and using Rvest extracts the raw text from each and creates a dictionary. The keys contain the original URL and the values contain the raw text output as parsed by Rvest.
-   `duster()`: Takes a vector of urls and uses the above two functions to create a tibble with the webpage identifiers as a index, the raw url, and the raw text from the webpage with extra line breaks removed.
-   `bow()`: Takes a string text as an input and returns the vector of unique words it contains.

## Installation

You can install the development version of BrokkR from [GitHub](https://github.com/UBC-MDS/BrokkR) with:

``` r
# install.packages("devtools")
devtools::install_github("UBC-MDS/BrokkR")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(BrokkR)
## basic example code
```

